\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-03-17 doc/paper.tex
update benchmark numbers with Higgs two-loop corrections

FlexibleSUSY (version 0.5.3), Softsusy (version 3.4.0), SPheno

@@

and gfortran 4.8.0.  SPheno and SPhenoMSSM were compiled with Intel
ifort 13.1.3 20130607\footnote{We are using Intel's ifort compiler,
  instead of gfortran 4.8.0, because it decreases the run-time of

@@

    FlexibleSUSY 0.5.3    & $0.151\unit{s}$    & $0.114\unit{s}$   & $0.081\unit{s}$\\
    Softsusy 3.4.0        & $0.178\unit{s}$    & $0.174\unit{s}$   & $0.157\unit{s}$\\
    SPheno 3.2.4          & $0.120\unit{s}$    & $0.118\unit{s}$   & $0.108\unit{s}$\\
    SPhenoMSSM 4.1.0${}^*$ & $0.463\unit{s}$    & $0.450\unit{s}$   & $0.403\unit{s}$\\

@@

    with g++ 4.8.0 and gfortran 4.8.0.  SPheno and SPhenoMSSM were

@@

    ${}^*$ SPhenoMSSM was generated with SARAH 4.1.0 and linked

@@

$0.120\unit{s}$, and FlexibleSUSY is second with $0.151\unit{s}$.  In

@@

$0.114\unit{s}$ and $0.081\unit{s}$, respectively.  The reason is that

>>>>

FlexibleSUSY (version 0.5.4), Softsusy (version 3.4.0), SPheno

@@

and Intel ifort 13.1.3 20130607.  SPheno and SPhenoMSSM were compiled
with Intel ifort 13.1.3 20130607\footnote{We are using Intel's ifort
  compiler, instead of gfortran, because it decreases the run-time of

@@

    FlexibleSUSY 0.5.4    & $0.151\unit{s}$    & $0.114\unit{s}$   & $0.091\unit{s}$\\
    Softsusy 3.4.0        & $0.174\unit{s}$    & $0.169\unit{s}$   & $0.162\unit{s}$\\
    SPheno 3.2.4          & $0.119\unit{s}$    & $0.115\unit{s}$   & $0.108\unit{s}$\\
    SPhenoMSSM 4.1.0${}^*$ & $0.416\unit{s}$    & $0.401\unit{s}$   & $0.366\unit{s}$\\

@@

    with g++ 4.8.0 and ifort 13.1.3 20130607.
    SPheno, SPhenoMSSM were

@@

    ${}^*$SPhenoMSSM was generated with SARAH 4.1.0 and linked

@@

$0.119\unit{s}$, and FlexibleSUSY is second with $0.151\unit{s}$.  In

@@

$0.114\unit{s}$ and $0.091\unit{s}$, respectively.  The reason is that
